Weather Data Integration and Assimilation System\\

### 2020-02-21 method/sec_0_introduction.tex
Plagiarism microservices

To get an overall idea of the flow of weather prediction, let us look into one of the flows using in \acrshort{curw} \cite{CUrWSL2017SL}.
\dbc{Use CUrW-SL}
\gkc{FIXED}

@@

\paragraph{Integration}-- The system should capable of integrating data from different sources such as satellite data, high end, and low-end weather station, etc. And the system should be able to handle multidimensional spatial and temporal weather data efficiently and optimally. 
\subsubsection{Assimilation}
Then the system should be able to fulfill weather models varying data requirements. Also, those models reproduce a large set of redundant data, thus the system should store the bulk data while optimizing the disk space.
\paragraph{Dissemination}-- Then different users should be able to retrieve data as they required. Also, the users should be able to easy to search into the available that in the system base on timeseries metadata or based on Geo queries.

>>>>

To get an overall idea of the flow of weather prediction, let us look into one of the flows using at \acrshort{curw} \cite{CUrWSL2017SL}.
\dbc{Use CUrW-SL}
\gkc{FIXED}

@@

\subsubsection{Integration}
The system should capable of integrating data from different sources such as satellite data, high end, and low-end weather station, etc. And the system should be able to handle multidimensional spatial and temporal weather data efficiently and optimally. 
\subsubsection{Assimilation}
Then the system should be able to fulfill weather models varying data requirements. Also, those models reproduce a large set of redundant data, thus the system should store the bulk data while optimizing the disk space.
\subsubsection{Dissemination}
Then different users should be able to retrieve data as they required. Also, the users should be able to easy to search into the available that in the system base on timeseries metadata or based on Geo queries.

### 2020-02-21 method/sec_1-architectural_decisions.tex
Plagiarism microservices

The initial design of \acrshort{wdias} used the \acrfull{soa}. Moreover, it tried to use an \acrfull{esb} to integrate different modules, as \acrshort{esb} is acting as a common layer for all of the modules. By default, \acrshort{esb} also provides publisher/subscribe (pub/sub) capabilities.
\hl{Because} \acrshort{esb} \hl{mediators can be used to integrate the modules which are described in Section} \ref{subse:modules_weather_data_integration_sys}. 
\gkc{FIXED}
The \acrshort{esb} has the processing units called \emph{mediators}. A mediator can take a message, carry out some predefined actions on it, and output the modified message. These mediator capabilities can use to integrate the modules of a weather data system as shown in \cref{fi:wdia_components}. \acrshort{esb} also supports different transportation protocols such as HTTP and Web sockets. However, it turned out that \acrshort{esb} is not suitable for data streaming or bulk data processing. Also, \acrshort{esb} suffers from a single point of failure, as all the messages are going through a common bus and slower communication (cant use for transfer data).

In the second design phase of \acrshort{wdias}, we attempted to use the actor model using the AKKA framework \cite{HewittWhyModel} to overcome above \acrshort{esb} drawbacks. At the same time, we moved away from the \acrshort{soa} architecture design to the microservice architecture design. Thus we redesign the system architecture with decomposing into microservices and used actors to implement each microservice in the system. In that case, an actor or an actor with slave actors was a map to each microservice in \acrshort{wdias}. \acrshort{soa} focuses on imperative programming, whereas microservices architecture focuses on a responsive actor programming style using faster messaging mechanisms.

When compare to \acrshort{soa}, the microservice architecture has several advantages such as the following:
\begin{itemize}
    \item Follow the Single Responsibility principle
    \item Resilient/flexible as a failure in one service does not impact other services. If you have monolithic or bulky service errors in one service/module it can impact other modules/functionality.
    \item High scalable as demanding services can be deployed in multiple servers to enhance performance and keep away from other services so that they do not impact other services. It will be difficult to achieve the same with single, large monolithic service.
    \item Easy to enhance as dependencies are less. It is also easier to change and test.
    \item Low impact on other services as each service is independent. % service., this has less chance to impact other services
    \item Easy to understand since they represent a small piece of functionality
    \item Ease of deployment
\end{itemize}

@@

Containerization is an alternative to the virtualization that supports virtual machines or Hypervisors. It involves encapsulating or packaging up software code and all its dependencies so that it can run uniformly and consistently on any infrastructure \cite{IBMContainerizationExplained}. The concept of containerization and process isolation has emerged after the open-source Docker Engine \cite{DockerAppContainerization}, an industry standard for package software into standardized units for development, shipment, and deployment.

The \acrshort{wdias} is using \acrfull{k8s} as the container orchestration system which is an open-source tool for automating deployment, scaling, and management of containerized applications \cite{LinuxFoundationProduction-GradeKubernetes}. It groups containers that make up an application into logical units for easy management and discovery. While implementing the \acrshort{wdias}, we used \acrshort{k8s} as the container-orchestration system, to deploy each microservice as container and manage with providing scalability and availability.

\begin{figure}[htp]
    \centering
    \includegraphics[width=1\textwidth]{method/microservice/k8s_architecture_v3.jpg}
    \caption{\acrfull{k8s} architecture.}
    \label{fi:k8s_architecture}
\end{figure}
\cref{fi:k8s_architecture} gives an overall idea on the components of \acrshort{k8s},
\begin{itemize}
    \item Pods -- Cluster of containers that can group other container images in a single unit.
    \item Nodes -- the machines (VMs, physical servers, etc) in a cluster that runs your applications and cloud workflows.
    \item kubelet -- An agent that runs on each node in the cluster. It makes sure that containers are running in a pod.
    \item kube-proxy -- A network proxy that runs on each node in the cluster, and maintains network rules on nodes.
    \item Kubernetes master -- Responsible for maintaining the desired state for your cluster.
    \item etcd -- Consistent and highly-available key value store used as Kubernetes’ backing store for all cluster data.
\end{itemize}

Users can add much as required Nodes into the \acrshort{k8s} cluster, and \acrshort{k8s} manage and deploy applications as pods into cluster nodes.
Each microservice can deploy as a Pod which is a group of containerized applications. And \acrshort{k8s} able to scale as much as the user wants as described above.
By separating each microservice as a container, and running them as multiple pods inside the \acrshort{k8s} removes the tight coupling of microservices when compared to the actors. This preserves the independent nature of the microservices which allows to high scale the system.

>>>>

The initial design of \acrshort{wdias} used the \acrfull{soa}. Moreover, it tried to use an \acrfull{esb} to integrate different modules, as \acrshort{esb} is acting as a common layer for all of the modules. By default, \acrshort{esb} also provides publisher/subscribe (pub/sub) capabilities.
\hl{Because} \acrshort{esb} \hl{mediators can be used to integrate the modules which are described in Section} \ref{subse:modules_weather_data_integration_sys}. 
\gkc{FIXED below}
The \acrshort{esb} has the processing units called \emph{mediators}. A mediator can take a message, carry out some predefined actions on it, and output the modified message. These mediator capabilities can use to integrate the modules of a weather data system as shown in \cref{fi:wdia_components}. \acrshort{esb} also supports different transportation protocols such as HTTP and Web sockets. However, it turned out that \acrshort{esb} is not suitable for data streaming or bulk data processing. Also, \acrshort{esb} suffers from a single point of failure, as all the messages are going through a common bus and slower communication (cant use for transfer data).

In the second design phase of \acrshort{wdias}, we attempted to use the actor model using the AKKA framework \cite{HewittWhyModel} to overcome above \acrshort{esb} drawbacks. At the same time, we moved away from the \acrshort{soa} architecture design to the microservice architecture design. Thus we redesign the system architecture with decomposing into microservices and used actors to implement each microservice in the system. In that case, an actor or an actor with slave actors was a map to each microservice in \acrshort{wdias}. \acrshort{soa} focuses on imperative programming, while the microservices architecture focuses on a reactive actor programming style using faster messaging mechanisms.

When compare to \acrshort{soa}, the microservice architecture has several advantages such as the following:
\begin{itemize}
    \item Follow the principle of a single responsibility.
    \item Resilient / flexible because a failure of a service has no influence on other services. If you have monolithic or major service errors in a service / module, this can have an impact on other modules / functionalities.
    \item High scalability because demanding services can be implemented on different servers to improve performance and stay away from other services so that they do not affect other services. It will be difficult to achieve the same with a single large monolithic service.
    \item Easy to improve because the dependencies are less. It is also easier to change and test.
    \item Little impact on other services because each service is independent.
    \item Easy to understand because they represent a small functionality.
    \item Ease of deployment.
\end{itemize}

@@

Containerization is an alternative to virtualization that supports virtual machines or hypervisors. This includes encapsulating or grouping the software code and all its dependencies so that it can work uniformly and consistently in any infrastructure. \cite{IBMContainerizationExplained}. The concept of containerization and process isolation has emerged after the open-source Docker Engine \cite{DockerAppContainerization}, an industry standard for package software into standardized units for development, shipment, and deployment.

The \acrshort{wdias} is using \acrfull{k8s} as the container orchestration system which is an open-source tool for automating deployment, scaling, and management of containerized applications \cite{LinuxFoundationProduction-GradeKubernetes}. It groups the containers that make up an application into logical units for easy management and detection. While implementing the \acrshort{wdias}, we used \acrshort{k8s} as the container-orchestration system, to deploy each microservice as container and manage with providing scalability and availability.

\begin{figure}[htp]
    \centering
    \includegraphics[width=1\textwidth]{method/microservice/k8s_architecture_v3.jpg}
    \caption{\acrfull{k8s} architecture.}
    \label{fi:k8s_architecture}
\end{figure}
\cref{fi:k8s_architecture} gives an overall idea on the components of \acrshort{k8s},
\begin{itemize}
    \item pods -- Cluster of containers that can group other container images in a single unit.
    \item nodes -- The machines (VMs, physical servers, etc) in a cluster that runs your applications and cloud workflows.
    \item kubelet -- An agent that runs on each node in the cluster. It makes sure that containers are running in a pod.
    \item kube-proxy -- A network proxy that runs on each node in the cluster, and maintains network rules on nodes.
    \item kubernetes master -- Responsible for maintaining the desired state for your cluster.
    \item etcd -- Consistent and highly-available key value store used as Kubernetes’ backing store for all cluster data.
\end{itemize}

Users can add much as required Nodes into the \acrshort{k8s} cluster, and \acrshort{k8s} manage and deploy applications as pods into cluster nodes.
Each microservice can deploy as a pod which is a group of containerized applications. And \acrshort{k8s} able to scale as much as the user wants as described above.
By separating each microservice as a container, and running them as multiple pods inside the \acrshort{k8s} removes the tight coupling of microservices when compared to the actors. This preserves the independent nature of the microservices which allows to high scale the system.

### 2020-02-21 method/sec_3-microservice.tex
Plagiarism microservices

A microservice architecture style is an approach to developing a single application as a suite of small services, each running in its own process and communicating with lightweight mechanisms, often via providing \hl{a RESTful API}. These services are built around business capabilities and independently deployable by fully automated deployment machinery \cite{LewisMicroservices}. \hl{These services are implemented independently with minimizing the centralized dependencies. Thus each microservice may be written in different programming languages and use different data storage technologies}.

@@

When building communication endpoints, \hl{many architectural approaches are adding significant smart by providing different protocol supports and complex logic support via the endpoints.} As an example \acrshort{esb} support multiple protocols and endpoints can use complex logic. But microservice follows an alternative approach: \emph{Smart endpoints and dumb pipes} \cite{LewisMicroservicesPipes}.
Applications built from microservices aim to be as decoupled and as cohesive as possible. They own their domain logic and act more as filters in the classical Unix sense. After receiving a request, applying logic as appropriate and producing a response. And it uses simple RESTful protocols rather than complex protocols.
\dbc{RESTish or RESTful?}
\gkc{Yes. Changed.}

@@

\acrshort{microservice} prefer letting each service manages its database, either different instances of the same database technology, or entirely different database systems - an approach called \emph{Polyglot Persistence} \cite{LewisMicroservicesManagement}.

The idea is to keep each microservice’s persistent data private to that service and accessible only via its \acrshort{api}. 
There are a few different ways to keep a service's persistent data private.  It does not need to provision a database server for each service. For example, in the case of using a relational database then the following methods can be used to keep data private \cite{RichardsonMicroservicesService}:
\begin{itemize}
    \item \emph{Private tables per service} –- each service owns a set of tables that must only be accessed by that service
    \item \emph{Schema per service} –- each service has a database schema that private to that service
    \item \emph{Database server per service} -– each service has its database server.
\end{itemize}
\emph{Private tables per service} and \emph{schema per service} have the lowest overhead. Using a \emph{schema per service} is appealing since it makes ownership clearer. Some high throughput services might need their database server.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\hl{Distributed Transactions over Microservices}}
\label{subse:sagas}
To ensure loose coupling, each microservice better to have own database. Maintaining data consistency between services is a challenge because 2 phase-commit/distributed transactions is not an option for many applications. A service publishes an event when its data changes. Other services consume that event and update their data \cite{RichardsonMicroservicesSagas}. This is also called the \emph{Saga pattern}.

@@

\paragraph{X-axis Scaling}-- X-axis scaling consists of running multiple copies of an application behind a load balancer. If there are \textit{n} copies then each copy handles 1/\textit{n} of the load. This is a simple, commonly used approach to scaling a service.

\paragraph{Y-axis Scaling}-- Unlike the X-axis and Z-axis, which consist of running multiple, identical copies of the application, Y-axis axis scaling splits the application into multiple, different services. Each service is responsible for one or more closely related functions. There are a couple of different ways of decomposing the application into services.
\begin{itemize}
    \item verb-based decomposition. e.g., checkout.
    \item decompose the application by noun. e.g., customer management. 
    \item an application might use a combination of verb-based and noun-based decomposition.
\end{itemize}

@@

\paragraph{Z-axis Scaling}-- When using Z-axis scaling each server runs an identical copy of the code (similar to X-axis scaling). The big difference is that each server is responsible for only a subset of the data. 
Z-axis splits are commonly used to scale databases. Data is partitioned (a.k.a. sharded) across a set of servers based on an attribute of each record.

>>>>

A microservice architecture style is an approach to developing a single application as a package of small services, each working in their own process and communicating with lightweight mechanisms, often through the delivery of \hl{a RESTful API}. These services are built around commercial capacities and can be used independently by fully automated implementation machines \cite{LewisMicroservices}. \hl{These services are implemented independently with minimizing the centralized dependencies. Thus each microservice may be written in different programming languages and use different data storage technologies}.

@@

When building communication endpoints, \hl{many architectural approaches are adding significant smart by providing different protocol supports and complex logic support via the endpoints.} As an example \acrshort{esb} support multiple protocols and endpoints can use complex logic. But microservice architecture follows an alternative approach called as \emph{Smart endpoints and dumb pipes} \cite{LewisMicroservicesPipes}.
Applications built on the basis of microservices are intended to be as disconnected and as coherent as possible. They have their domain logic and work more like filters in the classical Unix meaning. After receiving a request, apply the correct logic and produce a response. And it uses simple RESTful protocols instead of complex protocols.
\dbc{RESTish or RESTful?}
\gkc{Yes. Changed.}

@@

\acrshort{microservice} prefers to have each service manage its database, either different instances of the same database technology or entirely different database systems - an approach called \emph{Polyglot Persistence} \cite{LewisMicroservicesManagement}.

The idea is to keep the persistent data of each microservice private for this service and only to make it accessible via the \acrshort{api}.
There are different ways to keep the permanent data of a service private. It is not necessary to set up a database server for each service. For example, when you use a relational database, the following methods can be used to keep the data private. \cite{RichardsonMicroservicesService}:
\begin{itemize}
    \item \emph{Private tables per service} –- each service has a set of tables that this service should not have access to.
    \item \emph{Schema per service} –- each service has a private database schedule for this service.
    \item \emph{Database server per service} -– each service has its database server.
\end{itemize}
\emph{private tables per service} and \emph{schedule per service} have the lowest overhead. The use of an \emph{schedule per service} is interesting because it makes the property clearer. Some high throughput services may require their database server.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\hl{Distributed Transactions over Microservices}}
\label{subse:sagas}
To guarantee a loose coupling, every microservice can have its own database. Maintaining data consistency between services is a challenge because 2 phase-commit/distribution transactions are not an option for many applications. A service publishes an event when the data changes. Other services use this event and update their data \cite{RichardsonMicroservicesSagas}. This is also called the \emph{Saga pattern}.

@@

\paragraph{X-axis Scaling}-- When scaling the X-axis, multiple instances of an application execute behind a load balancer. If there are \textit{n} copies then each copy handles 1/\textit{n} of the load. A commonly used simple approach to scaling a service.

\paragraph{Y-axis Scaling}-- When compared to the Z-axis and X-axis scaling, which follows the concept of running multiple identical copies of the application, but Y-axis axis scaling segregate the application into multiple services in same domain. So, the end services are responsible for one or more closely related functions. There are different ways to split the application into services.
\begin{itemize}
    \item verb-based decomposition. e.g., checkout.
    \item decompose the application by noun. e.g., order management. 
    \item it possible to use a combination of verb-based and noun-based decomposition for an application.
\end{itemize}

@@

\paragraph{Z-axis Scaling}-- The Z-axis scaling is following the concept of each service runs an same application code (similar to X-axis scaling). The big difference is that each service is responsible for only a subset of the data. 
Z-axis splits are commonly used to scale databases. Data is partitioned (a.k.a. sharded) across a set of servers based on an attribute of each record.

### 2020-02-21 method/sec_5-data_preprocess.tex
Plagiarism microservices

The data imported via import modules may have incorrect data, missing data and not compatible with direct feed into simulation modules. 
Thus it required to preprocess the data before use it. The WDIAS supports these capabilities via the \emph{extension} modules. The current system has a few inbuilt extensions such as Interpolation, Transformation, and Validation. Other than those, it possible to add more extensions as required.
\begin{figure}[htp]
    \centering
    \includegraphics[width=0.5\textwidth]{method/data_preprocess/weather_data_preprocessing.jpg}
    \caption{\hl{Generic mathematical function model for weather data preprocessing}}
    \label{fi:weather_data_preprocessing}
\end{figure}

@@

\subsection{Interpolation}
The Interpolation module generates data at desired locations or desired points in time using either a serial or spatial interpolation technique. It is applied for the filling in of data gaps in measured on-line data, as well as to derive spatially distributed data for meteorological time series, such as precipitation and temperature, based on information available at neighboring locations.

>>>>

The data imported via import modules may have incorrect data, missing data and not compatible with direct feed into simulation modules. 
Thus it required to preprocess the data before use it. The WDIAS supports these capabilities via the \emph{extension} modules. The current system has a few inbuilt extensions such as Interpolation, Transformation, and Validation. Other than those, it possible to add more extensions as required.
\begin{figure}[htp]
    \centering
    \includegraphics[width=0.5\textwidth]{method/data_preprocess/weather_data_preprocessing.jpg}
    \caption{\hl{Weather data preprocessing using a generic mathematical function model}}
    \label{fi:weather_data_preprocessing}
\end{figure}

@@

\subsection{Interpolation}
The interpolation module generates data at desired locations or at desired data points using a serial or spatial interpolation technique. It is used to fill gaps in on-line measured data, and to derive spatially distributed data for weather time series, such as precipitation and temperature, based on information available at nearby locations.
